Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-18 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Draft code for precipitation validation

```{r}

```

>>>>

```{r}
my_hurricanes <- c("Floyd-1999", 
                   #"Irene-2011", 
                   #"Lee-2011", 
                   #"Ike-2008", 
                   #"Faye-2014",
                   #"Allison-2001")
my_day <- c(-3, -2, -1, 0, 1, 2, 3)
for(day in my_day){
        exposed <- map_counties(storm = "Floyd-1999", metric = "rainfall", 
                        days_included = day)
        tracks <- map_tracks(storm = "Floyd-1999", 
                        plot_object = exposed)
        print(tracks)
}
for(day in my_day){
        exposed <- map_counties(storm = "Irene-2011", metric = "rainfall", 
                        days_included = day)
        tracks <- map_tracks(storm = "Irene-2011", 
                        plot_object = exposed)
        print(tracks)
}
for(day in my_day){
        exposed <- map_counties(storm = "Lee-2011", metric = "rainfall", 
                        days_included = day)
        tracks <- map_tracks(storm = "Lee-2011", 
                        plot_object = exposed)
        print(tracks)
}
for(day in my_day){
        exposed <- map_counties(storm = "Ike-2008", metric = "rainfall", 
                        days_included = day)
        tracks <- map_tracks(storm = "Ike-2008", 
                        plot_object = exposed)
        print(tracks)
}
for(day in my_day){
        exposed <- map_counties(storm = "Allison-2001", metric = "rainfall", 
                        days_included = day)
        tracks <- map_tracks(storm = "Allison-2001", 
                        plot_object = exposed)
        print(tracks)
}
```
